### 2014-07-23 Quality_Reports/Strand_exploration.Rmd
Added function of how to the coverage was calculated

```{r show_df,include = TRUE,echo = FALSE,results = "asis"}
kable(design,format = "markdown")
kable(betaF,format = "markdown")
```

>>>>

```{r show_df,include = TRUE,echo = FALSE,results = "asis"}
kable(design,format = "markdown")
```

Using the following function, we generated the strand coverage across for all peaks, for all data sets. The coverage was calculated using the function:

```{r coverage_fun,include = TRUE,results = "hide",echo = TRUE}
strand_coverage <- function(reads,peak,st, fragLen = 0)
{
  reads = as(reads,"GRanges")
  reads = subset(reads, subset = strand(reads) == st)
  if(fragLen >0){
    reads = resize(reads,fragLen)
  }
  match = subjectHits(findOverlaps(peak,reads))
  cover = coverage(reads[match])[[1]]
  x = seq(start(peak),end(peak))
  if(nrun(cover) == 1){
    y = rep(runValue(cover),length(x))
  }else{
    xp = cumsum(runLength(cover)[1:(nrun(cover)-1)])
    yp = runValue(cover)
    y = stepfun(xp,yp)(x)
  }
  return(y)
}
```
